\section{Background and Pricing Model}
\label{sec:background}

We briefly recap what each paradigm delivers and how it is billed
because the cost analysis in \cref{sec:results-cost} pivots on these
formulas. All numbers are us-east-1 on-demand prices as published in
April~2026~\cite{aws-price-ec2,aws-price-fargate,aws-price-lambda,aws-price-ddb}.

\paragraph{EC2 (Auto Scaling Group).} A single \texttt{t3.small}
instance bills at \$0.0208 per running hour, regardless of utilisation.
Auto Scaling adds and removes machines according to a target-tracking
policy on average CPU. The policy in our deployment targets 50\%
average CPU; CloudWatch evaluates it every minute. New machines need
roughly the launch time of the AMI plus the warm-up period before they
join the load balancer.

\paragraph{ECS Fargate.} A Fargate task is billed per vCPU-second and
per GB-second of memory. For our 0.5\,vCPU + 1\,GB task this works out
to $0.5{\times}\$0.04048 + 1{\times}\$0.004445 = \$0.0247$ per task-hour.
Fargate scales by adding ECS tasks, which bypass the EC2 host
provisioning step but still require pulling the container image and
warming up the worker.

\paragraph{Lambda (container image).} A Lambda invocation is billed at
\$0.20 per million requests plus \$0.0000166667 per GB-second of
execution. With a 1\,GB function and a $\overline{t}$\,ms median
execution time, the per-request cost is
$2{\times}10^{-7} + \overline{t}{\times}10^{-3} \cdot 1.667{\times}10^{-5}$
USD. There is no charge while the container is warm but idle, but the
\emph{first} request after a cold gap pays the container init cost.
Optional provisioned concurrency keeps $N$ containers warm and is
billed at \$0.0000041667 per GB-second per provisioned worker.

\paragraph{ALB and DynamoDB.} The Application Load Balancer is billed at
\$0.0225 per hour plus \$0.008 per LCU-hour. Because all three
deployments share one ALB and the LCU charge is small at our test
scales, we treat the ALB cost as a constant in the cost model and not
as part of the per-paradigm comparison. DynamoDB on-demand at
\$1.25 per million writes and \$0.25 per million reads contributes a
constant per-request cost that we attribute equally to all three
paradigms.

\paragraph{Why the same image on all three.} A common pitfall in
multi-paradigm comparisons is to deploy code that is subtly different
across the targets, biasing latency or memory footprint measurements.
We use the AWS Lambda Web Adapter~\cite{lambda-web-adapter} to make a
single OCI image work on all three platforms: on EC2 and Fargate the
container starts gunicorn directly, and on Lambda the same gunicorn
process is fronted by the adapter so that incoming Lambda invocations
are translated into HTTP requests to \texttt{localhost:8080}. This
ensures the measured differences trace to the runtime, not to the
application code.
