\section{Discussion and Threats to Validity}
\label{sec:discussion}

\paragraph{Where each paradigm wins.} Our measurements line up with the
mental model practitioners report~\cite{eismann2021review} but make it
sharper. In the measured regime, \textbf{Lambda is the right answer
any time $\rho \lesssim 17\text{--}19$\,RPS}: its per-invocation billing wipes out
EC2's and Fargate's always-on cost, and the latency distribution is
strictly tighter. \textbf{EC2 becomes the right answer as soon as the
traffic is predictable and pre-provisionable}: a single t3.small holds a
13\,ms median at 100\,RPS, and multi-instance autoscaling straightens
out the tail above that. \textbf{Fargate's niche is narrower than its
marketing suggests}: at the smallest CPU size (0.5\,vCPU) a single task
cannot absorb even 100\,RPS of Python work, and task-level autoscaling
with the default 30\,s cooldown is too slow to catch a two-minute burst.
A larger task size (1--2\,vCPU) would push Fargate's saturation point
higher but also push its baseline cost closer to EC2's.

\paragraph{Cold start matters less than our probe could measure.}
Our cold-start scenario gapped requests by 60\,seconds, which was
insufficient to force Lambda to reclaim an idle execution environment.
All twelve probe samples landed in the warm 28--48\,ms band. The one
genuine cold start we captured --- the first request immediately after
\texttt{tofu apply} --- ran 4.3\,s end-to-end. A principled cold-start
study needs inter-request gaps of 5--15\,minutes sustained over
multiple instances; we flag this as future work and lean on prior
measurements~\cite{peeking-serverless, mcgrath-faas} where we need a
characterisation of the cold tail.

\paragraph{Threats to validity.}
\textit{(i)~Single region, single availability zone.} All numbers were
taken in \texttt{us-east-1a}; a different AZ would not change the
qualitative picture but might shift cold-start medians.
\textit{(ii)~Lambda quota ceiling.} A new AWS account carries a default
account-wide Lambda concurrency limit of 10. At our measured
$\overline{t}$~$\approx$~30\,ms this corresponds to a theoretical
ceiling of 333\,RPS, but the safe regime where we see no queueing is
closer to 75\,RPS --- and that is the ceiling we respected. A Lambda
comparison at 400\,RPS would require a service-quota increase.
\textit{(iii)~Load-generator host size.} Our k6 worker is a single
\texttt{t3.small}. For the rates measured here this machine is
comfortably not the bottleneck (sub-10\,ms of CPU budget per second
even at 400\,RPS GET-redirect), but higher rates would need
distributed k6.
\textit{(iv)~Cost model uses public list prices.} Real workloads pay
significantly less for EC2 with Reserved Instances, Savings Plans, or
Spot pricing; the Lambda break-even therefore moves \emph{against}
Lambda once any commitment discount is applied.
\textit{(v)~Automated abuse detection on shared-tenant platforms.}
Our initial deployment in the Learner Lab was terminated by the
Vocareum abuse-detection layer mid-experiment. The triggering signal
appears to have been sustained Lambda fan-out from a cold-start probe
combined with four-hour loadgen uptime; the total sustained traffic
never exceeded 8\,Mbps, well below the 1\,Gbps threshold in AWS's
commercial EC2 Testing Policy~\cite{awsec2test}. Any performance study
conducted on shared educational or trial accounts should budget for
this risk.
