\section{Methodology}
\label{sec:methodology}

\subsection{Workload, scenarios, and tooling}

We use \texttt{k6 v1.0}~\cite{k6} as the load generator. It is run on
a dedicated \texttt{t3.small} EC2 instance in \texttt{us-east-1a}, the
same availability zone as the targets, so that network jitter to the
ALB is bounded by intra-AZ RTT (sub-millisecond in our pings). Each run
begins with a thirty-second warm-up phase during which we issue
50~serial requests against \texttt{/healthz} on each platform to make
sure the connection pools are full and any JIT state is hot.
Per-request timings are recorded in CSV and a JSON summary (with
bootstrapped percentile statistics) is recorded at the end. The four
scenarios are:

\begin{description}[leftmargin=1em,labelindent=0pt,itemsep=2pt]
\item[Steady-state RPS sweep.] Constant arrival rate at
      $\{50, 100, 200, 400\}$ RPS for 120\,s each on EC2 and Fargate,
      and $\{25, 50, 75\}$ for 90\,s each on Lambda. The Lambda ceiling
      is dictated by our AWS account's default concurrency quota of 10
      simultaneous invocations; at 30\,ms of execution per request that
      implies a theoretical ceiling of 333\,RPS, but we stay safely
      below it.
\item[Step-arrival burst.] One minute at 5\,RPS, three minutes at the
      target rate, one minute back at 5\,RPS. The target is 400\,RPS
      for EC2/Fargate and 75\,RPS for Lambda.
\item[Cold-start probe.] One virtual user issues twelve sequential
      \texttt{/healthz} GETs with 60-second gaps. As we report in
      Section~\ref{sec:results-cold}, this gap turned out to be too short to
      reliably induce a Lambda container reclaim; our probe therefore
      characterises warm-path latency rather than cold-start tail.
\item[Mixed read/write.] 70\,\% GET-redirect, 30\,\% POST-shorten at
      200\,RPS (150\,RPS for Lambda) for three minutes; representative
      of a real shortener's traffic mix.
\end{description}

\subsection{Statistics}

Per-request raw latency is highly non-normal (heavy right tail), so we
report distribution percentiles rather than mean$\pm$sd. Confidence
intervals on each percentile are computed by non-parametric bootstrap
with $B{=}1000$ resamples and $\alpha{=}0.05$. The error bars in
Figure~\ref{fig:steady} are these intervals.

\paragraph{Time-to-steady-state.} We define the elasticity of a
deployment as the elapsed time between the start of the burst and the
first one-second bin whose p95 latency falls within $1.2\times$ of the
\emph{post-transient steady value}, where the steady value is the
median of the last 20\,\% of the burst window. Whenever no such bin
exists --- which only happens for Lambda when burst RPS exceeds the
account concurrency limit --- we record $\infty$.

\paragraph{Cost model.} The cost analysis combines the AWS billing
formulas of Section~\ref{sec:background} with our measured median execution
time. Concretely, for sustained $\rho$ RPS, our cost-per-month
(USD) is
\begin{equation}
\label{eq:cost}
\begin{aligned}
C_{\text{EC2}}      &= n(\rho)\cdot p_{\text{ec2}}\cdot T \\
C_{\text{Fargate}}  &= n(\rho)\cdot (v\cdot p_{\text{vCPU}} + g\cdot p_{\text{GB}})\cdot T \\
C_{\text{Lambda}}   &= \rho\cdot T\cdot
                       \bigl(p_{\text{req}} + g\cdot \overline{t}\cdot p_{\text{GB-s}}\bigr) + p_{\text{PC}}
\end{aligned}
\end{equation}

with $n(\rho)$ the steady-state number of compute units required to
sustain $\rho$ RPS at our measured saturation throughput, $T$ the
month-hours, $\overline{t}$ the median execution time of a request,
$g{=}1$\,GB and $v{=}0.5$ vCPU. Because DynamoDB and the ALB
contribute the same cost to all three paradigms, we report the
\emph{compute-only} cost when comparing them.
